Towards Practical First-Order Model Counting

### 2024-03-07 doc/paper.tex
Minor changes

\todo[inline,caption={}]{
  \begin{itemize}
    \item mention/describe the arithmetic simplification code
    \item (in Fig. 1) Crane2 doesn't use Crane, it uses itself
    \item describe which compilation rules are currently greedy or non-greedy
    \item my agenda has a plan for proving completeness for $\mathbf{C}^{2}$
  \end{itemize}
}

@@

\section{Smoothing}

@@

\todo[inline]{ Can I prove that the additions to smoothing outlined in the rest
  of this section `do the right thing'? }

@@

\begin{description}
  \item[\texttt{Ref}:] during smoothing, when unit clauses (a.k.a.\ variables)
        are propagated in the opposite direction of the FCG arcs (i.e.,
        `upwards'), when visiting a \texttt{Ref} node, these clauses are
        translated using the domain map of the \texttt{Ref} node. For example,
        if the domain map include $\Delta \mapsto \Delta'$, and the unit clause
        mentions $\Delta$, then replace it by $\Delta'$.
  \item[Constraint removal:] do reverse constraint removal. Assuming that
        domain $\Delta$ with constraints $X \ne c$ (for some constant
        $c \in \Delta$) were replaced with domain $\Delta'$, replace each
        $\forall X \in \Delta'\text{. }\phi(X)$ with
        $\forall X \in \Delta\text{. }X \ne c \Rightarrow \phi(X)$.
  \item[Domain recursion:] nothing special needs to be done (just propagate the
        union of the two sets of unit clauses upwards), assuming that $P(c)$ and
        $\forall X \in \Delta\text{. }X \ne c \Rightarrow P(X)$ are
        automatically combined into $\forall X \in \Delta\text{. }P(X)$.
\end{description}

>>>>

\todo[inline,caption={}]{
  \begin{itemize}
    \item mention/describe the arithmetic simplification code
    \item (in Fig. 1) Crane2 doesn't use Crane, it uses itself
    \item describe which compilation rules are currently greedy or non-greedy
    \item my agenda has a plan for proving completeness for $\mathbf{C}^{2}$
    \item Can I prove that Crane's domain recursion can always simulate
          ForcLift's domain recursion?
  \end{itemize}
}

@@

\section{Smoothing (only relevant for domain recursion v3)}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item Can I prove that the additions to smoothing outlined in the rest of
          this section `do the right thing'?
    \item I could include more info about the smoothing algorithm that didn't
          make it into the previous paper.
  \end{itemize}
}

@@

\begin{description}
  \item[\texttt{Ref}:] during smoothing, when unit clauses (a.k.a.\ variables)
        are propagated in the opposite direction of the FCG arcs (i.e.,
        `upwards'), when visiting a \texttt{Ref} node, these clauses are
        translated using the domain map of the \texttt{Ref} node. For example,
        if the domain map include $\Delta \mapsto \Delta'$, and the unit clause
        mentions $\Delta$, then replace it by $\Delta'$.
  \item[Constraint removal:] do reverse constraint removal. Assuming that
        domain $\Delta$ with constraints $X \ne c$ (for some constant
        $c \in \Delta$) were replaced with domain $\Delta'$, replace each
        $\forall X \in \Delta'\text{. }\phi(X)$ with
        $\forall X \in \Delta\text{. }X \ne c \Rightarrow \phi(X)$.
  \item[Domain recursion:] we merge $P(c)$ and $\forall X \in \Delta\text{.
        }X \ne c \Rightarrow P(X)$ into $\forall X \in \Delta\text{. }P(X)$.
        NOTE: the clauses may have other constraints, variables, etc. I could
        describe this more formally.
\end{description}
